Constraining Quiescent Supermassive Black Hole Environments.

### 2014-09-16 ms.tex
Update ms.tex

Constraints on the SMBH accretion rates at the low end of the SMBH
mass function also have implications for the black occupation
fraction.  For example, \citealt{MillerGallo+:2014a} used an observed
relation between $\Mbh$ and nuclear x-ray luminosity $L_x$ to
constrain the BH occupation fraction.  However, they extrapolate
(assuming a single power law) their observed relationship below their
detection threshold.  However, it is possible that the $L_x$-$\Mbh$
relationship steepens at smaller $\Mbh$, and thus the black hole
occupation fraction could be underestimated at low $\Mbh$.
% AG: In our model we obtain a steeper relationship, but we have difficulty matching the observed relationship above the detection threshold

>>>>

Constraints on the SMBH accretion rates at the low end of the SMBH
mass function also have implications for the black occupation
fraction.  For example, \citealt{MillerGallo+:2014a} used an observed
relation between $\Mbh$ and nuclear X-ray luminosity $L_x$ to
constrain the BH occupation fraction.  However, they extrapolate
(assuming a single power law) their observed relationship below their
detection threshold.  However, it is possible that the $L_x$-$\Mbh$
relationship steepens at smaller $\Mbh$, and thus the black hole
occupation fraction could be underestimated at low $\Mbh$.
% AG: In our model we obtain a steeper relationship, but we have difficulty matching the observed relationship above the detection threshold
